Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-25 paper.tex
new depth data (temp)

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 29.953518) (2, 36.796839) (3, 43.879808) (4, 50.748666) (5, 57.841152) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 130.215285) (2, 115.646322) (3, 125.256110) (4, 111.167837) (5, 110.668739)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 99.132787) (2, 106.834506) (3, 114.863343) (4, 122.601670) (5, 130.616379) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 573.555837) (2, 559.131666) (3, 568.973041) (4, 550.852189) (5, 551.364258)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.728805) (2, 17.909194) (3, 23.324666) (4, 28.030819) (5, 33.279611)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.841305) (2, 12.801791) (3, 13.358389) (4, 13.200611) (5, 13.251902)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 81.546486) (2, 85.345444) (3, 90.532347) (4, 98.247764) (5, 105.423875)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.539097) (2, 24.432485) (3, 25.629666) (4, 23.935250) (5, 23.911139)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 32.192292) (2, 39.246833) (3, 47.596875) (4, 53.228625) (5, 60.162625)
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 75.599833) (2, 94.688208) (3, 113.647292) (4, 131.776291) (5, 148.492917) 
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 101.828250) (2, 111.354459) (3, 115.116500) (4, 125.602792) (5, 130.459292) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 235.018833) (2, 319.038292) (3, 421.737083) (4, 522.937000) (5, 604.252875) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 12.507986) (2, 17.695611) (3, 22.835264) (4, 27.568305) (5, 32.235500) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 7.969861) (2, 8.940027) (3, 10.796555) (4, 11.887569) (5, 13.822249) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 76.545402) (2, 82.492861) (3, 88.691375) (4, 94.362653) (5, 98.254972) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 11.640499) (2, 15.205833) (3, 18.346361) (4, 21.828027) (5, 24.862680) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}
